Finite-state morphological transducers for three Kypchak languages

### 2014-03-22 kipchak-lrec-2013/kipchak-paper.tex
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51069 72bbbca6-d526-0410-a7d9-f06f51895060

Other analysers for Turkic languages---such as \texttt{TRmorph} \citep{coltekin2010}---approach this 
problem by positing a zero-derivation rule by which any noun can be `derived' into an adjective or 
an adverb, any adjective can be `derived' into a noun or adverb, etc.

@@

There are certain lexemes that require more explicit categorisation, for example, the word 
for `today'\footnote{Tatar: бүген; Kazakh: бүгін; Kumyk: бугюн. The word is etymologically composed of the words for `this' and `day'.} 
cannot be used attributively in Kypchak languages without the presence of an extra morpheme -KI. Compound nouns
using possessive morphology, such as Kazakh ауа райы `weather', do not take additional morphology the same way other substantives in the language do, due to the presence of a final possessive morpheme (e.g., ‹ауа райынан› `weather-\tags{abl}', not *‹ауа райыдан›). %FIXME: Explain the compound 'weather'.

>>>>

Other analysers for Turkic languages---such as \texttt{TRmorph} \citep{coltekin2010}---approach this 
problem by allowing a zero-derivation by which any noun can be `derived' into an adjective or 
an adverb, any adjective can be `derived' into a noun or adverb, etc.

@@

There are certain lexemes that require more explicit categorisation, for example, the word 
for `today'\footnote{Tatar: бүген; Kazakh: бүгін; Kumyk: бугюн. The word is etymologically composed of the words for `this' and `day'.} 
cannot be used attributively in Kypchak languages without the presence of an extra morpheme -KI. Compound nouns
using possessive morphology, such as Kazakh ауа райы `weather' (lit. `air condition'), do not take additional morphology the same way other substantives in the language do, due to the presence of a final possessive morpheme (e.g., ‹ауа райынан› `weather-{\sc abl}', not *‹ауа райыдан›). %FIXME: Explain the compound 'weather'.
